Vision and Cognitive Systems Final Project

### 2020-07-01 Paper_Presentation/paper/paper.tex
update delle 2:14
fine

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Orb_matches/match3.png}}
\caption{Orb matches}
\label{fig_Orb_matches}
\end{figure}
\bigskip

Likely, there will be a number of other false positives within similar distances due to the high dimensionality of the feature space.\\
In our implementation we reject all matches in which the distance ratio is greater than 0.75.
This allows us to keep the number of correctly retrieved paintings still high but at the same time to decrease the number of false positives.
A ranking with the 5 best matches found is then created and saved to a CSV file to show the results.
To understand if the painting is actually recognized among those in the DB, the average of the key points matched among the best 5 is calculated; if the first one differs from it for more than a certain value, it is considered correct and shown on the interface.\\

\section{Painting Rectification}
\subsection{Four points transform}
Over the contour found with the techniques described in \textbf{Precision boosting and paintings segmentation} is applied the function approxPolyDP from OpenCV to approximate it to a polygonal curve.\\
If the shape returned has four vertices we can assume that the process has found a rectangular painting.\\
Given the four points, we are able to estimate the homography and apply the transformation to rectify the painting.\\
To calculate the aspect ratio for the projected rectangle we use an implementation based on this paper \cite{b10} which derives the equations assuming a pinhole camera model.\\
This pipeline is applied to the paintings that don't get a match on the database.

@@

\begin{table}[htbp]
\caption{Performances}
\begin{center}
\begin{tabular}{|c|c|}
\hline
\textbf{} & \textbf{\textit{Paintings}} \\
\hline
TP& 161/210\\
\hline
FP& 20/210\\
\hline
FN& 29/210\\
\hline
Average IoU& 0.860\\
\hline
Average Precision& 0.909\\
\hline
Average Recall& 0.906\\
\hline
Average F-Measure& 0.904\\
\hline
\end{tabular}
\label{tab1}
\end{center}
\end{table}

@@

\begin{thebibliography}{00}
\bibitem{b1} C. Tomasi and R. Manduchi, "Bilateral filtering for gray and color images," Sixth International Conference on Computer Vision (IEEE Cat. No.98CH36271), Bombay, India, 1998, pp. 839-846, doi: 10.1109/ICCV.1998.710815..
\bibitem{b2} J. Zhang and J. Hu, "Image Segmentation Based on 2D Otsu Method with Histogram Analysis," 2008 International Conference on Computer Science and Software Engineering, Hubei, 2008, pp. 105-108, doi: 10.1109/CSSE.2008.206.
\bibitem{b3}Suzuki, S., and Be, K. (1985). Topological structural analysis of digitized binary images by border following. Computer Vision, Graphics, and Image Processing 30, 32–46. doi:10.1016/0734-189X(85)90016-7.
\bibitem{b4} \url{https://docs.opencv.org/2.4/modules/imgproc/doc/structural_analysis_and_shape_descriptors.html#approxpolydp}
\bibitem{b5} E. Rublee, V. Rabaud, K. Konolige and G. Bradski, "ORB: An efficient alternative to SIFT or SURF," 2011 International Conference on Computer Vision, Barcelona, 2011, pp. 2564-2571, doi: 10.1109/ICCV.2011.6126544.
\bibitem{b6}Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.
\bibitem{b7}Tareen, Shaharyar Ahmed Khan, and Zahra Saleem. "A comparative analysis of sift, surf, kaze, akaze, orb, and brisk." 2018 International conference on computing, mathematics and engineering technologies (iCoMET). IEEE, 2018.
\bibitem{b8} \url{https://docs.python.org/3/library/pickle.html}
\bibitem{b9} Lowe, David G. "Distinctive image features from scale-invariant keypoints." International journal of computer vision 60.2 (2004): 91-110.
\bibitem{b10}Zhang, Zhengyou, and Li-Wei He. "Whiteboard scanning and image enhancement." Digital Signal Processing 17.2 (2007): 414-432.
\bibitem{b11}Lin TY. et al. (2014) Microsoft COCO: Common Objects in Context. In: Fleet D., Pajdla T., Schiele B., Tuytelaars T. (eds) Computer Vision – ECCV 2014. ECCV 2014. Lecture Notes in Computer Science, vol 8693. Springer, Cham
\bibitem{b12} \url{https://docs.python.org/3/library/tkinter.html}

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Orb_matches/match3.png}}
\caption{Orb matches}
\label{fig_Orb_matches}
\end{figure}

Likely, there will be a number of other false positives within similar distances due to the high dimensionality of the feature space.
In our implementation we reject all matches in which the distance ratio is greater than 0.75.
This allows us to keep the number of correctly retrieved paintings still high but at the same time to decrease the number of false positives.
A ranking with the 5 best matches found is then created and saved to a CSV file to show the results.
To understand if the painting is actually recognized among those in the DB, the average of the key points matched among the best 5 is calculated; if the first one differs from it for more than a certain value, it is considered correct and shown on the interface.\\

\section{Painting Rectification}
\subsection{Four points transform}
Over the contour found with the techniques described in \textbf{Precision boosting and paintings segmentation} is applied the function approxPolyDP from OpenCV to approximate it to a polygonal curve.\\
If the shape returned has four vertices we can assume that the process has found a rectangular painting.\\
Given the four points, we are able to estimate the homography and apply the transformation to rectify the painting.\\
To calculate the aspect ratio for the projected rectangle we use an implementation based on this paper \cite{b10} which derives the equations assuming a pinhole camera model.\\
Another method based on the work done at PyImageSearch\cite{b13} is used in order to rectificate the painting given the four points of the contour.

@@

\begin{table}[htbp]
\caption{Performances}
\begin{center}
\begin{tabular}{|c|c|}
\hline
\textbf{} & \textbf{\textit{Paintings}} \\
\hline
TP& 161/236\\
\hline
FP& 31/236\\
\hline
FN& 44/236\\
\hline
Average IoU& 0.860\\
\hline
Average Precision& 0.855\\
\hline
Average Recall& 0.844\\
\hline
Average F-Measure& 0.845\\
\hline
\end{tabular}
\label{tab1}
\end{center}
\end{table}

@@

\begin{thebibliography}{00}
\bibitem{b1} C. Tomasi and R. Manduchi, "Bilateral filtering for gray and color images," Sixth International Conference on Computer Vision (IEEE Cat. No.98CH36271), Bombay, India, 1998, pp. 839-846, doi: 10.1109/ICCV.1998.710815..
\bibitem{b2} J. Zhang and J. Hu, "Image Segmentation Based on 2D Otsu Method with Histogram Analysis," 2008 International Conference on Computer Science and Software Engineering, Hubei, 2008, pp. 105-108, doi: 10.1109/CSSE.2008.206.
\bibitem{b3}Suzuki, S., and Be, K. (1985). Topological structural analysis of digitized binary images by border following. Computer Vision, Graphics, and Image Processing 30, 32–46. doi:10.1016/0734-189X(85)90016-7.
\bibitem{b4} \url{https://docs.opencv.org/2.4/modules/imgproc/doc/structural_analysis_and_shape_descriptors.html#approxpolydp}
\bibitem{b5} E. Rublee, V. Rabaud, K. Konolige and G. Bradski, "ORB: An efficient alternative to SIFT or SURF," 2011 International Conference on Computer Vision, Barcelona, 2011, pp. 2564-2571, doi: 10.1109/ICCV.2011.6126544.
\bibitem{b6}Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.
\bibitem{b7}Tareen, Shaharyar Ahmed Khan, and Zahra Saleem. "A comparative analysis of sift, surf, kaze, akaze, orb, and brisk." 2018 International conference on computing, mathematics and engineering technologies (iCoMET). IEEE, 2018.
\bibitem{b8} \url{https://docs.python.org/3/library/pickle.html}
\bibitem{b9} Lowe, David G. "Distinctive image features from scale-invariant keypoints." International journal of computer vision 60.2 (2004): 91-110.
\bibitem{b10}Zhang, Zhengyou, and Li-Wei He. "Whiteboard scanning and image enhancement." Digital Signal Processing 17.2 (2007): 414-432.
\bibitem{b11}Lin TY. et al. (2014) Microsoft COCO: Common Objects in Context. In: Fleet D., Pajdla T., Schiele B., Tuytelaars T. (eds) Computer Vision – ECCV 2014. ECCV 2014. Lecture Notes in Computer Science, vol 8693. Springer, Cham
\bibitem{b12} \url{https://docs.python.org/3/library/tkinter.html}
\bibitem{b13} \url{https://www.pyimagesearch.com/2014/08/25/4-point-opencv-getperspective-transform-example/}
